### 2021-04-09 ch03_esmvaltool/esmvaltool.tex
Further style optimization

The second main element of the \ac{ESMValTool} workflow is the calculation of
\emph{diagnostics}. This task is performed by the diagnostic scripts, which can
be written in multiple programming languages. Currently, the languages Python,
NCL, R, and Julia are supported. The diagnostic scripts, which contain the code
that runs the actual scientific evaluation, read the preprocessed datasets from
\ac{ESMValCore} and use these to create the final output of the tool. Apart
from \ac{NetCDF} files and plots, this includes log files with provenance
information that ensure the reproducibility and transparency of the results.
The whole workflow of the \ac{ESMValTool} is controlled with the \emph{recipe},
which is a configuration file in which the user can specify the desired input
datasets, preprocessing operations, and diagnostic scripts. Implementing a new
scientific assessment into the \ac{ESMValTool} usually includes writing a new
recipe and one or more diagnostic scripts. A third major element of the
\ac{ESMValTool} is the \emph{\acs{CMOR}ization} (\ie{} the reformatting of data
so it adheres to \ac{CMOR} standards) of raw observational datasets (not shown
in \cref{fig:03:esmvaltool_schematic}). This ensures that the \ac{ESMValTool}
can process arbitrary observational datasets, which can, for example, be used
to assess the skill of climate model simulations. More details on the structure
of the \ac{ESMValTool} are given in its extensive documentation
(\url{https://docs.esmvaltool.org}).

>>>>

The second main element of the \ac{ESMValTool} workflow is the calculation of
\emph{diagnostics}. This task is performed by the diagnostic scripts, which can
be written in multiple programming languages. Currently, the languages Python,
NCL, R, and Julia are supported. The diagnostic scripts, which contain the code
that runs the actual scientific evaluation, read the preprocessed datasets from
\ac{ESMValCore} and use these to create the final output of the tool. Apart
from \ac{NetCDF} files and plots, this includes log files with provenance
information that ensure the reproducibility and transparency of the results.
The whole workflow of the \ac{ESMValTool} is controlled with the \emph{recipe},
which is a configuration file in which the user can specify the desired input
datasets, preprocessing operations, and diagnostic scripts. Implementing a new
scientific assessment into the \ac{ESMValTool} usually includes writing a new
recipe and one or more diagnostic scripts. A third major element of the
\ac{ESMValTool} is the \emph{\acs{CMOR}ization} (\ie{} the reformatting of data
so it adheres to \ac{CMOR} standards) of raw observational datasets (not shown
in \cref{fig:03:esmvaltool_schematic}). This ensures that the \ac{ESMValTool}
can process arbitrary observational datasets, which can be used, for example,
to assess the skill of climate model simulations. More details on the structure
of the \ac{ESMValTool} are given in its extensive documentation
(\url{https://docs.esmvaltool.org}).
